Effects of gluon kinematics and the Sudakov form factor on the GBW and BGK saturation models

### 2023-04-23 Paper/draft.tex
plots udated

\usepackage[english]{babel}
\usepackage[a4paper]{geometry}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{breqn}
\usepackage[]{fancyhdr}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cite}
%\usepackage{times}
%\usepackage{merriweather}
%\usepackage{draftwatermark}
%\usepackage[backend=biber, style=ieee]{biblatex}

@@

\begin{figure}[p]
  \begin{multicols}{2}
    \includegraphics[width=0.47\textwidth]{./plots/GBW-dipole.png}
    \includegraphics[width=0.47\textwidth]{./plots/GBW-gluon.png}
    \includegraphics[width=0.47\textwidth]{./plots/GBW-saturation.png}\par
    \includegraphics[width=0.47\textwidth]{./plots/BGK-dipole.png}
    \includegraphics[width=0.47\textwidth]{./plots/BGK-gluon.png}
    \includegraphics[width=0.47\textwidth]{./plots/BGK-saturation.png}
  \end{multicols}
  \caption{The dipole cross section, the dipole gluon density at $x=10^{-2},
  10^{-6}$, and the saturation scale for the GBW (left) and the BGK (right)
  models Note, the dipole cross section and the gluon density are normalized by
  $\sigma_0^{-1}$. \comment{Larger y and x labels}} 
\end{figure}

>>>>

\usepackage[english]{babel}
\usepackage[a4paper]{geometry}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{breqn}
\usepackage[]{fancyhdr}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{ulem}
%\usepackage{times}
%\usepackage{merriweather}
%\usepackage{draftwatermark}
%\usepackage[backend=biber, style=ieee]{biblatex}

@@

\begin{figure}[p]
  \begin{multicols}{2}
    \includegraphics[width=0.49\textwidth]{./plots/GBW-dipole.pdf}
    \includegraphics[width=0.49\textwidth]{./plots/GBW-gluon.pdf}
    \includegraphics[width=0.49\textwidth]{./plots/GBW-saturation.pdf}\par
    \includegraphics[width=0.49\textwidth]{./plots/BGK-dipole.pdf}
    \includegraphics[width=0.49\textwidth]{./plots/BGK-gluon.pdf}
    \includegraphics[width=0.49\textwidth]{./plots/BGK-saturation.pdf}
  \end{multicols}
  \caption{The dipole cross section, the dipole gluon density at $x=10^{-2},\;
  10^{-6}$, and the saturation scale for the GBW (left) and the BGK (right)
  models Note, the dipole cross section and the gluon density are normalized by
  $\sigma_0^{-1}$. \sout{\comment{Larger y and x labels}}} 
\end{figure}
